DeepSched: A Deep Representation Of Scheduling Policies For Heterogeneous Distributed Systems

### 2020-04-09 paper/core/methodology.tex
added experimental setup section

The targeted \emph{fitness function} will be the average waiting time $W_t$ for all tasks. The fitness function for a specific schedule \emph{S} is given by:
\begin{equation}
\mathcal Fitness(S) = \frac{\sum_{i=1}^{N} W_{ti}}{N}
\end{equation}

@@

@@

\begin{figure}[hp]
    \centering
    \includegraphics[width=0.45\textwidth]{diagrams/sched_nn}
    \caption{The architecture of the proposed neural network for distributed heterogeneous systems scheduling}
    \label{fig:nn}
\end{figure}

\subsubsection{Objective Function}
The cost function defined for this architecture is a sum of two criteria. Categorical cross entropy \emph{(CE)} on the predicted machine to run a specific job $M_p$ and mean square error \emph{(MSE)} on the predicted actual start time $AST_p$ and the predicted actual finish time $AFT_p$. So it can be summarized as follows:
\begin{equation}
\mathcal Loss(L) = CE(M_p, M_t) + MSE(AT_p, AT_t)
\end{equation}
where $M_p$ is the predicted machine, $M_t$ is the ground truth machine, $AT_p$ is the predicted actual time range and $AT_t$ is the ground truth actual time range. \\

>>>>

The targeted \emph{fitness function} is the average waiting time $W_t$ for all tasks. The fitness function for a specific schedule \emph{S} is given by:
\begin{equation}
\mathcal Fitness(S) = \frac{\sum_{i=1}^{N} W_{ti}}{N} \label{eq:ga}
\end{equation}

@@

\begin{figure}[hp]
    \centering
    \includegraphics[width=0.45\textwidth]{diagrams/sched_nn}
    \caption{The architecture of the proposed neural network (DeepSched) for distributed heterogeneous systems scheduling.}
    \label{fig:nn}
\end{figure}

@@

\subsubsection{Objective Function}
The cost function defined for this architecture is a sum of two criteria. Categorical cross entropy \emph{(CE)} on the predicted machine to run a specific job $M_p$ and mean square error \emph{(MSE)} on the predicted actual start time $AST_p$ and the predicted actual finish time $AFT_p$. So it can be summarized as follows:
\begin{equation}
\mathcal Loss(L) = CE(M_p, M_t) + MSE(AT_p, AT_t) \label{eq:l}
\end{equation}
where $M_p$ is the predicted machine, $M_t$ is the ground truth machine, $AT_p$ is the predicted actual time range and $AT_t$ is the ground truth actual time range. \\
